---
name: Jens Daniel
surname: Müller
position: "Postdoctoral Researcher"
profilepic: portrait_JDM_square.jpg
address: "ETH Zurich | Department of Environmental Systems Science"
www: jens-daniel-mueller.github.io
email: "jensdaniel.mueller@usys.ethz.ch"
twitter: Jens_D_Mueller
github: jens-daniel-mueller
orcid: 0000-0003-3137-0883
headcolor: 005f73
date: "`r format(Sys.time(), '%B %Y')`"
csl: "csl/copernicus-publications_jdm.csl"
output:
  vitae::awesomecv:
    page_total: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(tidyverse)
library(vitae)
```

# Brief bio

My name is Jens and I'm currently doing my second PostDoc at ETH Zurich. My scientific focus is on marine biogeochemistry, meaning I try to understand how organisms - including homo technicus - shape their chemical environment, and vice versa. To do so, I enjoy wrangling, visualizing, synthesizing and thereby understanding data obtained mainly from autonomous observatories such as voluntary observing ships, floats and buoys. If the CO2 content of seawater is involved in one way or another, this makes me even more happy.

# Most relevant publications
# Education

```{r}

tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where, ~Why,
  
  "PhD Chemical Oceanography", 
  "07 / 2014 – 06 /2018", 
  "Leibniz-Institute for Baltic Sea Research Warnemünde (IOW)", 
  "Warnemünde, Germany",
  c("Ocean Acidification in the Baltic Sea: Involved Processes, Metrology of pH in Brackish Waters, and Calcification under Fluctuating Conditions",
    "Grade: With honors (Summa cum laude)"),
  
  "MSc Biological Oceanography", 
  "09 / 2010 – 08 / 2012", 
  "GEOMAR Helmholtz Centre for Ocean Research Kiel", 
  "Kiel, Germany",
  "Grade: 1.2 (ECTS grade, A Excellent)",

  "BSc Chemistry", 
  "09 / 2008 – 08 / 2009", 
  "Phillips-University Marburg", 
  "Marburg, Germany",
  "Grade: 1.7 (ECTS grade B “Very good”)"
) %>%
  detailed_entries(Institution, Year, Degree, Where, Why)
```


# Employment

```{r}

tribble(
  ~ Role,
  ~ Year,
  ~ Institution,
  ~ Where,
  ~ Details,
  
  "Postdoctoral researcher",
  "07 /2020 - present",
  "ETH Zürich",
  "Zurich, Switzerland",
  "Environmental Physics | Prof. Dr. Nicolas Gruber",
  
  "Postdoctoral researcher",
  "07 / 2018 – 06 /2020",
  "Leibniz-Institute for Baltic Sea Research Warnemünde (IOW)",
  "Warnemünde, Germany",
  "Trace gas biogeochemistry | Prof. Dr. Gregor Rehder",
  
  "Scientific Employee",
  "10 / 2013 – 03 / 2014",
  "GEOMAR Helmholtz Centre for Ocean Research Kiel",
  "Kiel, Germany",
  c(
    "Benthic Ecology | Prof. Dr. M. Wahl",
    "Marine Biogeochemistry | Prof. Dr. U. Riebesell"
  ),
  
  "Sailing Instructor",
  "07 – 10 / 2013 ",
  "Kiel Marketing GmbH | Camp 24/7",
  "Kiel, Germany",
  c(),
  
  "Divemaster",
  "01 – 03 / 2013",
  "Al Dive dive centre",
  "Loubiere, Dominica",
  c(),
  
  "Research Assistant",
  "05 – 08 / 2010",
  "GEOMAR Helmholtz Centre for Ocean Research Kiel",
  "Kiel, Germany",
  "Evolutionary Ecology of Marine Fishes | Prof. Dr. T. Reusch"
  
) %>%
  detailed_entries(Institution, Year, Role, Where, Details)


```

# Publications

## Peer reviewed

```{r}

bibliography_entries("publication_list_jdm.bib") %>%
  filter(type == "article-journal")


```

## In review

```{r}

bibliography_entries("publication_list_jdm.bib") %>%
  filter(type == "report")


```

## Books

```{r}

bibliography_entries("publication_list_jdm.bib") %>%
  filter(type == "book")


```

## Thesis

```{r}

bibliography_entries("publication_list_jdm.bib") %>%
  filter(type == "thesis")


```

## Datasets

```{r}

bibliography_entries("publication_list_jdm.bib") %>%
  filter(type == "")


```

# Teaching
# Honors