---
name: Jens Daniel
surname: Müller
position: "Postdoctoral Researcher"
pronouns: he/his
address: "ETH Zurich | Department of Environmental Systems Science"
www: jens-daniel-mueller.github.io
email: "jensdaniel.mueller@usys.ethz.ch"
twitter: Jens_D_Mueller
github: jens-daniel-mueller
date: "`r format(Sys.time(), '%B %Y')`"
csl: "csl/copernicus-publications_jdm.csl"
output:
  vitae::awesomecv:
    page_total: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(tidyverse)
library(vitae)
```

# Brief bio

My name is Jens and I'm currently doing my second PostDoc at ETH Zurich. My scientific focus is on marine biogeochemistry, meaning I try to understand how organisms - including homo technicus - shape their chemical environment, and vice versa. To do so, I enjoy wrangling, visualizing, synthesizing and thereby understanding data obtained mainly from autonomous observatories such as voluntary observing ships, floats and buoys. If the CO2 content of seawater is involved in one way or another, this makes me even more happy.

# Education

```{r}
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where,
  "Informal studies", "1889-91", "Flying University", "Warsaw, Poland",
  "Master of Physics", "1893", "Sorbonne Université", "Paris, France",
  "Master of Mathematics", "1894", "Sorbonne Université", "Paris, France"
) %>%
  detailed_entries(Degree, Year, Institution, Where)
```

# Nobel Prizes

```{r}
tribble(
  ~Year, ~Type, ~Desc,
  1903, "Physics", "Awarded for her work on radioactivity with Pierre Curie and Henri Becquerel"
) %>%
  brief_entries(
    glue::glue("Nobel Prize in {Type}"),
    Year,
    Desc
  )
```

# Publications

## Peer reviewed

```{r}

bibliography_entries("publication_list_jdm.bib") %>%
  filter(type == "article-journal")


```

## In review

```{r}

bibliography_entries("publication_list_jdm.bib") %>%
  filter(type == "report")


```

## Books

```{r}

bibliography_entries("publication_list_jdm.bib") %>%
  filter(type == "book")


```

## Thesis

```{r}

bibliography_entries("publication_list_jdm.bib") %>%
  filter(type == "thesis")


```

## Datasets

```{r}

bibliography_entries("publication_list_jdm.bib") %>%
  filter(type == "")


```
