---
name: Jens Daniel
surname: Müller
position: "Postdoctoral Researcher"
profilepic: portrait_JDM_square.jpg
address: "ETH Zurich | Department of Environmental Systems Science"
www: jens-daniel-mueller.github.io
email: "jensdaniel.mueller@usys.ethz.ch"
twitter: Jens_D_Mueller
github: jens-daniel-mueller
orcid: 0000-0003-3137-0883
aboutme: Ocean biogeochemist with a favour for carbon & observations seasoned with data science
headcolor: 005f73
date: "`r format(Sys.time(), '%B %Y')`"
csl: "csl/copernicus-publications_jdm.csl"
output:
  vitae::awesomecv:
    page_total: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(tidyverse)
library(vitae)
```

# About

I'm a biogeochemists studying the ocean carbon cycle through measurements of CO~2~ in seawater. Since 2020, I work as a PostDoc with Nicolas Gruber at ETH Zurich. We use global ship-based observations to reconstruct the [accumulation of CO~2~ in the global ocean](https://doi.org/10.22541/essoar.167525217.76035050/v1), and how this drives acidification in the ocean interior. This work profits from the experience gained during my PhD, specifically the development of pH analytics, the analysis of autononmous pCO~2~ measurements from a voluntary observing ship and several months spend at sea. As a coordinator of [RECCAP2](https://reccap2-ocean.github.io/) - the second cycle of the REgional Carbon Cycle Assessment and Processes project - I'm working with an international board of around 100 scientists covering a broad view on the ocean carbon sink through models and surface flux estimates.

# Key publications

```{r}

pub_list_formatted <- 
bibliography_entries("publication_list_jdm.bib") %>%
  mutate(title = str_replace(title,
                             "CO_",
                             "CO")) %>%
  mutate(title = str_replace(title,
                             "\\{2\\}",
                             "2")) %>%
  mutate(title = gsub("([\\])", "", title)) %>%
  mutate(title = str_replace(title,
                             "\\{textrm2\\}",
                             "2")) %>% 
  mutate(title = str_replace_all(title,
                             "CO2",
                             "CO~2~")) %>% 
  mutate(title = str_replace_all(title,
                             "pHT",
                             "pH~T~"))
  # mutate(author = str_replace(author, "Müller", "**Müller**"))

pub_list_formatted %>%
  filter(id %in% c("muller_long-term_2016",
                   "muller_metrology_2018",
                   "gruber_trends_2023",
                   "muller_decadal_2023",
                   "schneider_biogeochemical_2018"))


```

# Postdoctoral employment

```{r}

tribble(
  ~ Role,
  ~ Year,
  ~ Institution,
  ~ Where,
  ~ Details,
  
  "Postdoctoral researcher",
  "07 /2020 - present",
  "ETH Zurich",
  "Zurich, Switzerland",
  "Environmental Physics | Prof. Dr. Nicolas Gruber",
  
  "Postdoctoral researcher",
  "07 / 2018 – 06 /2020",
  "Leibniz-Institute for Baltic Sea Research Warnemünde (IOW)",
  "Warnemünde, Germany",
  "Trace gas biogeochemistry | Prof. Dr. Gregor Rehder",
  
  "Visiting scientist",
  "07 / 2019 – 06 /2020",
  "Max Planck Institute for Meteorology (MPI-M)",
  "Hamburg, Germany",
  "Observations, Analysis and Synthesis | Dr. Peter Landschützer"

) %>%
  detailed_entries(Institution, Year, Role, Where, Details)


```

# Education

```{r}

tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where, ~Why,
  
  "PhD Chemical Oceanography", 
  "07 / 2014 – 06 /2018", 
  "Leibniz-Institute for Baltic Sea Research Warnemünde (IOW)", 
  "Warnemünde, Germany",
  c("Ocean Acidification in the Baltic Sea: Involved Processes, Metrology of pH in Brackish Waters, and Calcification under Fluctuating Conditions",
    "Grade: With honors (Summa cum laude)"),
  
  "MSc Biological Oceanography", 
  "09 / 2010 – 08 / 2012", 
  "GEOMAR Helmholtz Centre for Ocean Research Kiel", 
  "Kiel, Germany",
  "Grade: 1.2 (ECTS grade, A Excellent)",

  "BSc Chemistry", 
  "09 / 2008 – 08 / 2009", 
  "Phillips-University Marburg", 
  "Marburg, Germany",
  "Grade: 1.7 (ECTS grade B “Very good”)"
) %>%
  detailed_entries(Institution, Year, Degree, Where, Why)
```

# Experiences

```{r}

tribble(
  ~ Role,
  ~ Year,
  ~ Institution,
  ~ Where,
  ~ Details,

  "Scientific Employee",
  "10 / 2013 – 03 / 2014",
  "GEOMAR Helmholtz Centre for Ocean Research Kiel",
  "Kiel, Germany",
  c(
    "Benthic Ecology | Prof. Dr. M. Wahl",
    "Marine Biogeochemistry | Prof. Dr. U. Riebesell"
  ),
  
  "Research Assistant",
  "05 – 08 / 2010",
  "GEOMAR Helmholtz Centre for Ocean Research Kiel",
  "Kiel, Germany",
  "Evolutionary Ecology of Marine Fishes | Prof. Dr. T. Reusch",
  
  "Certified Scientific Diver & Divemaster",
  "2011 - present",
  "200+ logged dives, dive mission leader, Nitrox-diver",
  "Global",
  c(
    "Off-shore mesocosm experiment, Gran Canaria, Spain (2 months)",
    "Huinay Scientific Field Station, Patagonia, Chile (3 months)",
    "Divemaster at Al Dive dive centre, Loubiere, Dominica (3 months)"
  ),
  
  "Research cruises",
  "2011 - 2020",
  "10 expeditions, 6 months at sea",
  "Baltic Sea",
  c(
    "RVs Elisabeth Mann Borgese, Aranda, Alkor & Litorina",
    "VOS Finnmaid",
    "SVs HRIMFARE & Littorina"
  ),
  
  "Sailor",
  "2010 - present",
  "Boat driver, safety and radio certificates",
  "Global",
  c("Member of the Academic Sailing Association in Kiel (ASViK e.V.)",
    "Several sailing campaigns including two ocean crossings",
    "Owner of SV Tina V (2019 - 2022)")
  
) %>%
  detailed_entries(Institution, Year, Role, Where, Details)


```

# Publications

## Peer reviewed

```{r}

pub_list_formatted %>%
  filter(type == "article-journal") %>%
  mutate(title = str_replace(title,
                             "CO_",
                             "CO")) %>%
  mutate(title = str_replace(title,
                             "\\{2\\}",
                             "2")) %>%
  mutate(title = gsub("([\\])", "", title)) %>%
  mutate(title = str_replace(title,
                             "\\{textrm2\\}",
                             "2")) %>% 
  mutate(title = str_replace_all(title,
                             "CO2",
                             "CO~2~")) %>% 
  mutate(title = str_replace_all(title,
                             "pHT",
                             "pH~T~"))


```

## In review

```{r}

pub_list_formatted %>%
  filter(type == "report")


```

## Books

```{r}

pub_list_formatted %>%
  filter(type == "book")


```

## Thesis

```{r}

pub_list_formatted %>%
  filter(type == "thesis")


```

## Datasets

```{r}

pub_list_formatted %>%
  filter(type == "")


```

## Selected conference presentations

# Teaching experience

```{r}


tribble(
  ~ Year,
  ~ Lecture,
  ~ Institution,
  ~ comment,
  ~ detail,
  
  "SS 2022 & SS 2023",
  "Global Biogeochemical Cycles and Climate (with Nicolas Gruber & Meike Vogt)",
  "ETH Zurich",
  "Tutorials:",
  c("Seawater chemistry",
    "Circulation of the ocean and atmosphere",
    "Ocean carbon cycle",
    "Terrestrial carbon cycle"),
  
  "SS 2019",
  "Analytical and Environmental Chemistry I (with Gregor Rehder)",
  "University of Rostock",
  "Lectures:",
  c("Dissolved Gases",
    "Water"),
  
  "WS 2018/19",
  "Analytical Chemistry IV: Environmental Chemistry (with Gregor Rehder)",
  "University of Rostock",
  "Lectures:",
  c("Dissolved Gases",
    "Current topic: Baltic Sea Biogeochemistry")
  
) %>%
  detailed_entries(comment, Year, Lecture, Institution, detail)




```

# Funding

```{r}


tribble(
  ~ Year,
  ~ Award,
  ~ Institution,
  ~ comment,
  ~ detail,
  
  "2019-2022",
  "SPECTROPHABS",
  "BSH",
  "Spectrophotometric pH-measurements for monitoring of marine acidification in the Baltic Sea",
  "co-applicant",
  
  "2018",
  "Early-Career Grant",
  "National Geographic Society",
  "Financial and outreach support for Bloomsail expedition",
  c(),
  
  "2010 - 2018",
  "Academic Scholarships",
  "German Academic Scholarship Foundation",
  "Multiple fundings granted independently",
  c(
    "PhD scholarship (ideational)",
    "Full student scholarship",
    "Field work grant, Patagonia, Chile",
    "Advanced English course, Bath, England",
    "Summer academy, San Giovanni, Italy"
  )
) %>%
  detailed_entries(comment, Year, Award, Institution, detail)


```

# Honors and Awards

```{r}

tribble(
  ~ Year, ~ Award, ~ Institution, ~comment,
  
"2019",
"Briese Award",
"Shipping company Briese",
"Outstanding PhD thesis in Marine Research",

"2019",
"Dissertation award",
"German Water Chemical Society",
"Outstanding PhD thesis in Water Chemistry, sponsored by Walter-Kölle foundation",

"2019",
"Dissertation award",
"Baltic Sea Research Foundation",
"Outstanding PhD thesis in Baltic Sea Science",

"2017",
"Best poster award",
"Baltic Sea Science Congress", 
"for presentation by newcomers",

"2005",
"Book-price",
"Bertha-von-Suttner Gymnasium",
"for extraordinary achievements during the Abitur",

) %>%
  detailed_entries(comment, Year, Award, Institution)



```
